R Notebook

### 2023-03-29 Analysis tests.Rmd
update structure

```{r}
df <- read_csv("data/test/funda_buy_21-03-2023(sample100p).csv")

@@

```{r}
model <- lm(data = df, price~room +living_area + house_age)
summary(model)
```

```{r}
df_new <- df %>% 
  separate(address_line, c("zip", "letters", "city", "optional1","optional2", "optional3", "optional4"), " ") %>% 
  mutate(addressline_city = paste(city, optional1, optional2, optional3, optional4),
         addressline_zip = paste(zip, letters),
         addresszip = paste0(address, ", ",addressline_zip, ", ", city, ", Nederland")) %>% 
  select(-optional1, -optional2, -optional3, -optional4) %>% 
  geocode(addresszip, method = 'osm', lat = latitude , long = longitude)
#write.csv(df_new,"data/funda_buy_21-03-2023(sample100p)latlon.csv")
#df_new %>% 
#  select(longitude, latitude, price, room, living_area, house_age) %>% 
#  write.csv("data/test/mgwr.csv")
```
```{r}

@@

df_sp <- df_new %>% drop_na()
x = st_as_sf(df_sp, coords = c( "longitude", "latitude"), crs = 4326)
x <- st_transform(x, crs = 28992)
st_write(x, "data/test/test_sample(100p).gpkg")
x <- st_read("data/test/test_sample(100p).gpkg")
```

>>>>

```{r}
df <- read_csv("Scraper/data/funda_buy_28-03-2023_full.csv")

@@

```{r}
model <- lm(data = df, price~ house_type + building_type + room + bedroom + bathroom + living_area + energy_label +has_balcony + has_garden + house_age)
summary(model)
```

```{r}
df_new <- df %>% 
  separate(address_line, c("zip", "letters", "city", "optional1","optional2", "optional3", "optional4"), " ") %>% 
  mutate(addressline_city = paste(city, optional1, optional2, optional3, optional4),
         addressline_zip = paste(zip, letters),
         addresszip = paste0(address, ", ",addressline_zip, ", ", city, ", Nederland")) %>% 
  select(-optional1, -optional2, -optional3, -optional4) %>% 
  geocode(addresszip, method = 'osm', lat = latitude , long = longitude)
#write.csv(df_new,"data/funda_buy_28-03-2023_full_latlon.csv")
#df_new %>% 
#  select(longitude, latitude, price, room, living_area, house_age) %>% 
#  write.csv("data/test/mgwr.csv")
```
```{r}
#write.csv(df_new,"data/funda_buy_28-03-2023_full_latlon.csv")
#df_sp <- df_new %>% drop_na()
#x = st_as_sf(df_sp, coords = c( "longitude", "latitude"), crs = 4326)
#x <- st_transform(x, crs = 28992)
#st_write(x, "data/funda_buy_28-03-2023_full.gpkg")

@@

#df_sp <- df_new %>% drop_na()
#x = st_as_sf(df_sp, coords = c( "longitude", "latitude"), crs = 4326)
#x <- st_transform(x, crs = 28992)
#st_write(x, "data/test/test_sample(100p).gpkg")
#x <- st_read("data/test/test_sample(100p).gpkg")
```
